\Title

### 2021-07-01 manuscript/content.tex
Revise the new gb random/sequential section

\subsection{
    Interpolating synthetic survey with gradient boosting
}
\label{sec:gb_interpolation}

Finally we used gradient-boosted equivalent sources to interpolate the
synthetic airborne survey. We started by locating a set of block-averaged
equivalent sources using a block size of \EqlBoostAirborneSpacing{} and, based
on the results presented on section \ref{sec:window_size_and_overlap}, we
decided to use an overlap of 50\% and a window size of
\EqlBoostAirborneWindowSize{} in order to define a considerable amount of
windows.

We estimated the \emph{depth} and \emph{damping} parameters by comparing the
predictions against the values of the target grid, exploring \emph{depth}
values between \EqlBoostAirborneMinDepth{} and \EqlBoostAirborneMaxDepth{} and
\emph{damping} values between \EqlBoostAirborneMinDamping{} and
\EqlBoostAirborneMaxDamping{} by steps of one order of magnitude.
The most accurate predictions achieved a RMS error of
\EqlBoostAirborneRmsScore{} with a depth of \EqlBoostAirborneDepth{} and
a damping of \EqlBoostAirborneDamping{}.

Figure~\ref{fig:eql-boost-airborne}a shows the differences between the target
grid and the predictions made by the gradient-boosted equivalent sources.
Figure~\ref{fig:eql-boost-airborne}b shows the RMS error of the
residuals after each iteration, exposing how the gradient-boosting algorithm
converges to a minimum fitting error.

Worth noting that the RMS error achieved by the gradient-boosted equivalent
sources is comparable to the values obtained by the regular equivalent sources
in Section \ref{sec:synthetic_distributions}.

@@

With the goal of highlighting the importance of randomizing the order in which
the overlapping windows are iterated, we interpolated the airborne synthetic
survey using the same estimated values for the \emph{damping} and
\emph{depth} but disabling the random shuffling of the windows, iterating over
them in sequential order.
Fig.~\ref{fig:eql-boost-airborne}c shows the differences between the target
grid and the predictions made by the gradient-boosted equivalent sources
without random shuffling the windows.
Fig.~\ref{fig:eql-boost-airborne}d shows the RMS error of the
residuals after each iteration.
These results show how the gradient-boosted equivalent sources underperform by
iterating over the overlapping windows in sequential order: they fail to
produce realistic and accurate predictions while the speed in which the
algorithm converges is smaller.

>>>>

\subsection{
    Interpolation with gradient boosting
}
\label{sec:gb_interpolation}

Finally, we applied the gradient-boosted equivalent sources to interpolate the
synthetic airborne survey (Fig.~\ref{fig:synthetic-layouts}).
As previously, we used the block-averaged sources layout with a block size of
\EqlBoostAirborneSpacing{}.
Based on the results from section \ref{sec:window_size_and_overlap}, we adopted
a window overlap of 50\% and a window size of \EqlBoostAirborneWindowSize{}.

We estimated the relative depth of the sources and the damping parameter by
comparing the predictions against the values of the target grid.
The search explored \emph{depth} values between \EqlBoostAirborneMinDepth{} and
\EqlBoostAirborneMaxDepth{} and \emph{damping} values between
\EqlBoostAirborneMinDamping{} and \EqlBoostAirborneMaxDamping{} by steps of one
order of magnitude.
The most accurate predictions achieved a RMS error of
\EqlBoostAirborneRmsScore{} with a depth of \EqlBoostAirborneDepth{} and
a damping of \EqlBoostAirborneDamping{}.
It is worth noting that the RMS error achieved by the gradient-boosted
equivalent sources is comparable to the ones obtained by the regular equivalent
sources in Section \ref{sec:synthetic_distributions}.
To highlight the importance of randomizing the order of windows in the
gradient-boosting iterations, we preformed the interpolation once more using
the same values of \emph{damping} and \emph{depth} but this time iterating over
windows in sequential order (South to North, West to East).

Figs.~\ref{fig:eql-boost-airborne}a-b show the differences between the target
grid and the interpolation results for windows in randomized and sequential
order, respectively.
The differences for randomized windows resemble those for regular least-squares
equivalent sources seen in Figs.~\ref{fig:ground-survey-differences} and
\ref{fig:airborne-survey-differences}.
On the other hand, the differences for sequential windows show a clear
trend of large negative differences in the South decreasing towards the North.
This trend is correlated with the order in which windows are executed, with
differences decreasing in absolute value towards the end of the algorithm.
Fig.~\ref{fig:eql-boost-airborne}c shows the RMS error of the fitting process
after each iteration for both window orders, clearly indicating that
a randomized window order leads to faster convergence of the algorithm.

@@
